PSE Quant Sampling Algorithm

### 2021-02-26 quant_estimate/pse_quant_algo.tex
Run : Manual Example Added

	// Probabilistic query : assert(P(c != d) < 0.5)
	// Opitimize here : 
	//	Optimal value of forall (a) such that P(c != d) is close to 0.5 	
	return 0;
}
\end{minted}

@@

>>>>

	// Probabilistic query : assert(P(c != d) < 0.5)
	// Optimize here : 
	//	Optimal value of forall (a) such that P(c != d) is close to 0.5 	
	return 0;
}
\end{minted}

@@

For the sample program given above, we first resort to using \texttt{symbolic execution} to generate \texttt{path constraints} for all the feasible paths that this program can take and then convert the \texttt{path constraints} into an \texttt{formal logic} optimization problem that gives an \texttt{assignment} to \texttt{forall} variables such that it leads to optimum violation of the $query$.

\begin{minted}{python}
def generateCandidates(k: int):
	opt = z3.Optimize()
	a = z3.Int("a_sym")
	d = z3.Int("d_prob_sym")

	opt.add(d >= 0)
	opt.add(d <= 650)
	opt.add(a > 50)
	opt.add(z3.Not(d > 60))
	opt.add(a + 75 > d)

	opt.maximize(a - d - 75) 	# Query to optimize
	n = 0
	while opt.check() == z3.sat and n != k:
		m = opt.model()
		n += 1
		print("%s = %s" % (a, m[a]))
		print("%s = %s" % (d, m[d]))
		opt.add(a != m[a])
\end{minted}
